\Large \bf Compilers Project: PTX Super-optimization

### 2018-04-29 paper/main.tex
more testing, paper reached 6pgs

@@

@@

>>>>

The current implementation uses the z3 solver and encodes the above in
bit-vector theory to capture the nature of the inputs.

@@

The program can also expand by modelling relevant parts in the theory of arrays
or floating-point theory.

@@

Additionally, the output-by-output processing can be
optimized. Certain outputs are clearly disjoint: finding
one would not aid in finding the other. In theory, by
trying to synthesize all pairs of outputs in either order,
we can determine which outputs are disjoint. This could let
us dramatically reduce the number of candidate programs.
The efficacy of this optimization relies on the idea that
if a pair of outputs is disjoint then one of the outputs
is disjoint to all outputs the other is not disjoint to.
Non-disjointness is best viewed in this usage as an equivalence
relation and disjointness its negation, verifying the above.
